\begin{publications}

    \section*{已发表论文}

    \begin{enumerate}
        \item \textbf{Yue Wu}， Steven C.H. Hoi， Tao Mei， and Nenghai Yu. ``
            Large-scale Online Feature Selection for Ultra-high Dimensional Sparse
            Data''， ACM Transactions on Knowledge Discovery from Data, 2017 (accepted).
        \item \textbf{Yue Wu}， Steven C.H. Hoi， Chenghao Liu， Jing Lu， Doyen Sahoo，
            and Nenghai Yu. “SOL: A Library for Scalable Online Learning
            Algorithms”， Neurocomputing， 2017 (accepted).
        \item \textbf{Yue Wu}， Xu Shen， Tao Mei， Xinmei Tian， Nenghai Yu， and Yong
            Rui. ``Monet: A System for Reliving Your Memories by Theme-Based Photo
            Storytelling''， \emph{IEEE Transactions on Multimedia}， vol. 18， no.
            11， pp. 2206-2216， Nov. 2016 (the first two authors contributed equally).
        \item \textbf{Yue Wu}， Tao Mei， Ying-Qing Xu， Nenghai Yu， and Shipeng Li.
            ``MoVieUp: Automatic Mobile Video Mashup''， \emph{IEEE Transactions on
            Circuits and Systems for Video Technology}， vol. 25， pp. 1941-1954， Dec
            2015.
        \item Jianlong Fu， \textbf{Yue Wu}， Tao Mei， Jinqiao Wang， Hanqing Lu， and
            Yong Rui. ``Relaxing from vocabulary: Robust weakly-supervised deep
            learning for vocabulary-free image tagging''， In Proceedings of the
            IEEE International Conference on Computer Vision(ICCV)， pp. 1985-1993，
            2015 (the first two authors are with equal contribution).
        \item \textbf{Yue Wu}， Shiyang Lu， Tao Mei， Jian Zhang， and Shipeng Li. ``Local visual
            words coding for low bit rate mobile visual search''， In Proceedings of
            the 20th ACM international conference on Multimedia (MM)， pp.  989-992，  ACM， 2012.
        \item Dayong Wang， Pengcheng Wu， Peilin Zhao， \textbf{Yue Wu}， Chunyan Miao， and
            Steven CH Hoi. ``High-dimensional data stream classification via sparse
            online learning''， In Data Mining (ICDM)， 2014 IEEE International
            Conference on(ICDM)， pp. 1007-1012. IEEE， 2014.
    \end{enumerate}

\end{publications}

